### 2018-09-17 sections/strategy_Htautau.tex
final version for conf

In the $\Htautau$ search, the $\ttbar \to WbHq$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson and at least four jets, only one of which originates from a $b$-quark.
%In the $\Htautau$ search, the final state signature of interest is characterised by the presence of two $\tau$-leptons from the
%decay of the Higgs boson as well as a light-quark jet, the latter two originating from the decay of one of the top quarks. 
If one of the $\tau$-leptons decays leptonically, an isolated electron or muon and significant $\met$ is also expected.
%The other top quark decays into a $W$ boson and a $b$-quark, with the $W$ boson in turn decaying hadronically, resulting in 
%three additional jets. Therefore, at least four jets are typically expected in signal events.
However, in a significant fraction of the events the lowest-$\pt$ jet from the $W$-boson decay fails the minimum $\pt$ requirement of $30~\gev$,
resulting in signal events with only three jets reconstructed.
In order to optimise the sensitivity of the search, the selected events are categorised into four SRs depending 
on the number of $\taulep$ and $\tauhad$ candidates, and on the number of jets:
($\lephad$, 3j), ($\lephad$, $\geq$4j), ($\hadhad$, 3j), and ($\hadhad$, $\geq$4j).

@@

Boosted decision trees (BDT)~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} are used in each SR to improve the separation between signal and background. 
%The separate training exploits differences in event kinematics across SRs.  
%draft 1 version
%In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
%whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
elsewhere the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account.

@@

\begin{itemize}
\item $m_{\tau\tau}^{\text{fit}}$: the invariant mass of the two $\tau$-lepton candidates after the reconstruction of the neutrinos, indicating the reconstructed Higgs boson mass.
\item $m_{Hq}$: the invariant mass of the reconstructed Higgs boson and the associated light-quark jet in the $t \to Hq$ decay, corresponding to the reconstructed mass of the parent top quark.
\item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\met$ in the $\lephad$ channel.
\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\tauhad$ candidate (denoted as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\tauhad$ candidates (denoted as particles 1 and 2 respectively) in the $\hadhad$ channel.
\item $\met$ $\phi$ centrality: a variable that quantifies the relative angular position of the $\mpt$ with respect to the 
visible tau decay products in the transverse plane. The transverse plane is transformed such that the direction of the tau decay products are 
orthogonal, and that the smaller angle between the tau decay products defines the positive quadrant of the transformed plane. 
The $\met$ $\phi$ centrality is defined as the sum of the $x$- and $y$-components of the $\mpt$ unit vector in this transformed plane.
%\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
%\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the transverse direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector, minus 
the magnitude of the fitted $\mpt$ vector.
\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector perpendicular to the fitted $\mpt$ vector.
\item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically-decaying $W$ boson.
\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance to the $\lep$ candidate.
\item $m_{\tau j}$: the invariant mass of the  $\tauhad$ candidate and the jet that has the smallest angular distance to the $\tauhad$ candidate.
\item $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$: the momentum fractions carried by the visible decay products from the two $\tau$-lepton candidates 
(whether $\taulep$ or $\tauhad$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
\item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$ boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark. This variable is only defined for events with at least four jets.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of some of the most
important BDT input variables in the $\lephad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
$p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\tauhad$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The first and the last bins in all figures contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
which is determined via a likelihood fit to data.}
\label{fig:BDT_inputs_lephad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of two of the most 
important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
$x_{1}^{\text{fit}}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
The contributions with real $\tauhad$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\tauhad$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The first and the last bins in the figures in (a) and (b) contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\tauhad$ background, 
which is determined via a likelihood fit to data.} 
\label{fig:BDT_inputs_hadhad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

In the $\Htautau$ search, the $\ttbar \to WbHq$ signal being probed is characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson and at least four jets, only one of which originates from a $b$-quark.
%In the $\Htautau$ search, the final state signature of interest is characterised by the presence of two $\tau$-leptons from the
%decay of the Higgs boson as well as a light-quark jet, the latter two originating from the decay of one of the top quarks. 
If one of the $\tau$-leptons decays leptonically, an isolated electron or muon and significant $\met$ is also expected.
%The other top quark decays into a $W$ boson and a $b$-quark, with the $W$ boson in turn decaying hadronically, resulting in 
%three additional jets. Therefore, at least four jets are typically expected in signal events.
However, in a significant fraction of the events the lowest-$\pt$ jet from the $W$-boson decay fails the minimum $\pt$ requirement of $30~\gev$,
resulting in signal events with only three jets reconstructed.
In order to optimise the sensitivity of the search, the selected events are categorised into four SRs depending 
on the number of $\taulep$ and $\had$ candidates, and on the number of jets:
($\lephad$, 3j), ($\lephad$, $\geq$4j), ($\hadhad$, 3j), and ($\hadhad$, $\geq$4j).

@@

Boosted decision trees (BDT)~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} are used in each SR to improve the separation between signal and background. 
%The separate training exploits differences in event kinematics across SRs.  
%draft 1 version
%In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\tauhad$ contributions), 
%whereas to obtain the result the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account. 
In the training, only $\ttbar \to W(qq)bH(\tau\tau)q$ signal events are used against the total SM background (including both real and fake $\had$ contributions), 
elsewhere the contributions from $\ttbar \to W(\ell\nu)bHq$ signal events are also taken into account.

@@

\begin{itemize}
\item $m_{\tau\tau}^{\text{fit}}$: the invariant mass of the two $\tau$-lepton candidates after the reconstruction of the neutrinos, indicating the reconstructed Higgs boson mass.
\item $m_{Hq}$: the invariant mass of the reconstructed Higgs boson and the associated light-quark jet in the $t \to Hq$ decay, corresponding to the reconstructed mass of the parent top quark.
\item $m_{\text{T,lep}}$: the transverse mass calculated from the lepton and $\met$ in the $\lephad$ channel.
\item $p_{\text{T,1}}$ and $p_{\text{T,2}}$:  the transverse momenta of the lepton and $\had$ candidate (denoted as particles 1 and 2 respectively) in the $\lephad$ channel, or the transverse momenta of the leading and trailing $\had$ candidates (denoted as particles 1 and 2 respectively) in the $\hadhad$ channel.
\item $\met$ $\phi$ centrality: a variable that quantifies the relative angular position of the $\mpt$ with respect to the 
visible tau decay products in the transverse plane. The transverse plane is transformed such that the direction of the tau decay products are 
orthogonal, and that the smaller angle between the tau decay products defines the positive quadrant of the transformed plane. 
The $\met$ $\phi$ centrality is defined as the sum of the $x$- and $y$-components of the $\mpt$ unit vector in this transformed plane.
%\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the parallel direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
%\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of $\mpt$ in the transverse direction in the transformed plane (see definition of $\met$ $\phi$ centrality).
\item $E_{\text{T},\parallel}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector parallel to the fitted $\mpt$ vector, minus 
the magnitude of the fitted $\mpt$ vector.
\item $E_{\text{T},\perp}^{\text{miss}}$: the magnitude of the projection of the original $\mpt$ vector perpendicular to the fitted $\mpt$ vector.
\item $m_{b j_1}$: the invariant mass of the $b$-jet and the leading jet candidate from the hadronically-decaying $W$ boson.
\item $m_{\text{lep}j}$: the invariant mass of the lepton and the jet that has the smallest angular distance to the $\lep$ candidate.
\item $m_{\tau j}$: the invariant mass of the  $\had$ candidate and the jet that has the smallest angular distance to the $\had$ candidate.
\item $x_{1}^{\text{fit}}$ and $x_{2}^{\text{fit}}$: the momentum fractions carried by the visible decay products from the two $\tau$-lepton candidates 
(whether $\taulep$ or $\had$) per event. It is based on the best-fit four-momentum of the neutrino(s) according to the event reconstruction procedure outlined in Section~\ref{sec:htautau_reco_cat}.
\item $m_{bj_1j_2}$: the invariant mass of the $b$-jet and the two jets originating from the $W$ boson in the $t\to Wb \to j_1j_2b$ decay, corresponding to the reconstructed mass of the parent top quark. This variable is only defined for events with at least four jets.
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_lephad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/ptL2_lephad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of some of the most
important BDT input variables in the $\lephad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\lephad$, 3j) region and (b) the ($\lephad$, $\geq$4j) region, and for
$p_{\text{T},2}$ in (c) the ($\lephad$, 3j)  region and (d) the ($\lephad$, $\geq$4j) region.
The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The first and the last bins in all figures contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
which is determined via a likelihood fit to data.}
\label{fig:BDT_inputs_lephad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\begin{center}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/m_tt_hadhad_4j_FR.eps}} \\
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_3j_FR.eps}}
\subfloat[]{\includegraphics[width=0.40\textwidth]{figures/Htautau/control_plots/x1_fit_hadhad_4j_FR.eps}} \\
\caption{$\Htautau$ search: Comparison between the data and background prediction after preselection for the distribution of two of the most 
important BDT input variables in the $\hadhad$ channel before performing the fit to data (``Pre-Fit''). The distributions are shown for
$m_{\tau\tau}^{\text{fit}}$ in (a) the ($\hadhad$, 3j) region and (b) the ($\hadhad$, $\geq$4j) region, and for
$x_{1}^{\text{fit}}$ in (c) the ($\hadhad$, 3j)  region and (d) the ($\hadhad$, $\geq$4j) region.
The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The expected $\Hc$ signal (solid red) corresponding to $\BR(t\to Hc)=1\%$ is also shown,
added on top of the background prediction.
The first and the last bins in the figures in (a) and (b) contain the underflow and overflow respectively.
The bottom panel displays the ratio of data to the SM background (``Bkg'') prediction.
The hashed area represents the total uncertainty on the background, excluding the normalisation uncertainty of the fake $\had$ background, 
which is determined via a likelihood fit to data.} 
\label{fig:BDT_inputs_hadhad}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-09-17 sections/systematic_uncertainties.tex
final version for conf

Uncertainties associated with electrons, muons, and $\tauhad$ candidates arise from the trigger, reconstruction,  
identification and isolation (in the case of electrons and muons) efficiencies, as well as the momentum scale and resolution. 
These are measured in data using $Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events ($\ell =e, \mu$)~\cite{ATLAS-CONF-2016-024,Aad:2016jkr} 
in the case of electrons and muons, and using $Z\to \tau^+\tau^-$ events in the case of $\tauhad$ candidates~\cite{ATLAS-CONF-2017-029}.

@@

Uncertainties on the data-driven fake $\tauhad$ background in the $\Htautau$ search are obtained by using additional signal-depleted regions. The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\tauhad$ identification criteria, and thus referred to as ``loose SR"  and ``loose CR". 
%The shape difference between the fake $\tauhad$ background prediction in each loose SR and its associated loose CR
%is applied as an uncertainty on the prediction in the nominal SR.
%In each loose SR, the shape difference between the data and the fake $\tauhad$ background estimate based on its associated loose CR,
%in both cases having subtracted the small contribution from real $\tauhad$ candidates based on the simulation, 
%is applied as an uncertainty on the prediction in the nominal SR. 
%In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty on the prediction in the nominal SR. 
In each loose SR, after subtracting the small contribution from real $\tauhad$ candidates based on the simulation, 
the relative difference in the shape of the distribution between the remaining data and the fake $\tauhad$ background estimate based on its associated loose CR 
is applied as an uncertainty on the prediction in the nominal SR.
In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\tauhad$ candidate from the simulation that are added to the fake $\tauhad$ template in the $\hadhad$ channel as part of the fake $\tauhad$ background estimation procedure (see Section~\ref{sec:faketaus}). This uncertainty, associated with the modelling of the fake $\tauhad$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\tauhad$ candidate. 
The same uncertainty is assigned to the selected signal events with fake $\tauhad$ candidates.
In addition, a systematic uncertainty is assigned to account for the different fractional composition of particles (various types of leptons and partons) originating the fake $\tauhad$ candidates 
between each SR and its corresponding CR in the $\ttbar$ simulation. 
Finally, the normalisation of the fake $\tauhad$ background in each SR is determined in the fit to data. 
%In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template. The MC studies shows that non-H-to-tautau signal with fake taus can contribute to the $\lephad$ channel. So a 30\% uncertainty is  applied to these signal-faking-tau events.

>>>>

Uncertainties associated with electrons, muons, and $\had$ candidates arise from the trigger, reconstruction,  
identification and isolation (in the case of electrons and muons) efficiencies, as well as the momentum scale and resolution. 
These are measured in data using $Z\to \ell^+\ell^-$ and $J/\psi\to \ell^+\ell^-$ events ($\ell =e, \mu$)~\cite{ATLAS-CONF-2016-024,Aad:2016jkr} 
in the case of electrons and muons, and using $Z\to \tau^+\tau^-$ events in the case of $\had$ candidates~\cite{ATLAS-CONF-2017-029}.

@@

Uncertainties on the data-driven fake $\had$ background in the $\Htautau$ search are obtained by using additional signal-depleted regions. The construction is similar to that of the SRs and corresponding CRs discussed in Section~\ref{sec:fakeleptons}, but employing further loosened $\had$ identification criteria, and thus referred to as ``loose SR''  and ``loose CR''. 
%The shape difference between the fake $\tauhad$ background prediction in each loose SR and its associated loose CR
%is applied as an uncertainty on the prediction in the nominal SR.
%In each loose SR, the shape difference between the data and the fake $\tauhad$ background estimate based on its associated loose CR,
%in both cases having subtracted the small contribution from real $\tauhad$ candidates based on the simulation, 
%is applied as an uncertainty on the prediction in the nominal SR. 
%In each loose SR, the shape difference between the data and the data-driven prediction of its associated loose CR is extracted and applied as an uncertainty on the prediction in the nominal SR. 
In each loose SR, after subtracting the small contribution from real $\had$ candidates based on the simulation, 
the relative difference in the shape of the distribution between the remaining data and the fake $\had$ background estimate based on its associated loose CR 
is applied as an uncertainty on the prediction in the nominal SR.
In addition, a 30\% uncertainty is applied to the fraction of $\ttbar$ events with a fake $\had$ candidate from the simulation that are added to the fake $\had$ template in the $\hadhad$ channel as part of the fake $\had$ background estimation procedure (see Section~\ref{sec:faketaus}). This uncertainty, associated with the modelling of the fake $\had$ rate by the simulation, is estimated by comparing data and simulation in a sample enriched in $\ttbar$ dilepton events plus a fake $\had$ candidate. 
The same uncertainty is assigned to the selected signal events with fake $\had$ candidates.
In addition, a systematic uncertainty is assigned to account for the different fractional composition of particles (various types of leptons and partons) originating the fake $\had$ candidates 
between each SR and its corresponding CR in the $\ttbar$ simulation. 
Finally, the normalisation of the fake $\had$ background in each SR is determined in the fit to data. 
%In order to be conservative, the yield of different origins of the fake taus is studied and a dedicated uncertainty is added to the fake template. The MC studies shows that non-H-to-tautau signal with fake taus can contribute to the $\lephad$ channel. So a 30\% uncertainty is  applied to these signal-faking-tau events.
